---
title: "Part C"
author: "Charlie Joey Hadley"
output: 
  pagedown::html_paged:
    toc: false
knit: pagedown::chrome_print
css: styles.css
bibliography: references.bib
csl: nature.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

# Report

Your .Rmd document must read in the dataset from the data folder.

```{r}
survey_data <- read_excel("data/survey-data.xlsx")
```

You must cite the dataset and paper using cross references. As an example, here is a reference for a paper on food pairings @ahn_flavor_2011.

You must use a {pagedown} format or template. This example document uses pagedown::html_paged with a limited amount of custom CSS. You do not need to customise the CSS for your report - you will not receive extra credit for a beautiful looking report.

Note that when you knit this document is also generates a PDF file with the same name as the RMarkdown document. You must include both the .Rmd and PDF file in your submission.

The lines below in this template demonstrate how to customise the appearance and position of the references, ie to add a heading.

# References

<div id="refs"></div>
